---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# synPUF

## Overview

This package contains a 50 person subset of the CMS 2008-2010 Data Entrepreneurs’ Synthetic Public Use File (DE-SynPUF) from OHDSI. 

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Details

* [Information on the SynPUF data source is available here](https://www.cms.gov/Research-Statistics-Data-and-Systems/Downloadable-Public-Use-Files/SynPUFs/DE_Syn_PUF.html)
* [CDM 5.2.2 DDL for the OHDSI supported DBMSs is available here](https://github.com/OHDSI/CommonDataModel/blob/v5.2.2/PostgreSQL/OMOP%20CDM%20ddl%20-%20PostgreSQL.sql)

Install the development version from [GitHub](https://github.com/thewileylab/synPUF) with:

``` r
# install.packages("devtools")
devtools::install_github("thewileylab/synPUF")
```
## Example

This is a basic example:

```{r example}
library(synPUF)
suppressMessages(library(tidyverse))
person
```

## Code of Conduct

Please note that the synPUF project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

